---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-",
  message = FALSE, 
  warning = FALSE
)

# R CMD build fda.usc.beta_2019_06_13
# R CMD INSTALL fda.usc_1.6.0.tar.gz
```
 


<!--
# fda.usc
README.md is generated from README.Rmd. Please edit that file 
#[![Travis-CI Build Status](https://api.travis-ci.org/maierhofert/classiFunc.svg?branch=master)](https://travis-ci.org/maierhofert/classiFunc)
#[![packageversion](https://img.shields.io/badge/Package%20version-0.1.1-orange.svg?style=flat-square)](https://CRAN.R-project.org/package=classiFunc)
[![CRAN_Status_Badge](https://www.r-pkg.org/badges/version/fda.usc)](https://cran.r-project.org/package=fda.usc)
[![](https://cranlogs.r-pkg.org/badges/fda.usc)](https://cran.r-project.org/package=fda.usc)
# [![Licence](https://img.shields.io/badge/licence-GPL--3-blue.svg)](https://www.gnu.org/licenses/gpl-3.0.en.html)
Incluir reference card
-->



## Package overview
The **fda.usc** package implements methods  for exploratory and descriptive analysis of functional data such as depth measurements, atypical curves detection, regression models, supervised classification, unsupervised classification and functional analysis of variance.


**fda.usc** package carries out exploratory and descriptive analysis of functional data exploring its most important features such as depth measurements or functional outliers detection, among others. It also helps to explain and model the relationship between a dependent variable and independent (regression models) and make predictions. Methods for supervised or unsupervised classification of a set of functional data regarding a feature of the data are also included. It can perform functional ANOVA,  hypothesis testing, functional response models and many others.


## Using fda.usc
For installation instructions, see below.

A hands on introduction to \code{fda.usc} can be found in the reference [vignette](https://www.jstatsoft.org/index.php/jss/article/view/v051i04/v51i04.pdf).

Details on specific functions are in the [reference manual](https://cran.r-project.org/package=fda.usc/fda.usc.pdf).

Manuel Oviedo PhD thesis [Advances in functional regression and classification models](http://hdl.handle.net/10347/18236)


## Issues & Feature Requests
For issues, bugs, feature requests etc. please use the [Github Issues](https://github.com/moviedo5/fda.usc/issues). Input is always welcome.

## Installation

You can install the current fda.usc version from CRAN with:

```{r cran-installation, eval = FALSE}
install.packages("fda.usc")
```


or the latest patched version from Github with:

```{r gh-installation, eval = FALSE,warning=FALSE,message=FALSE}
library(devtools)
devtools::install_github("moviedo5/fda.usc")
# devtools::install_github("moviedo5/fda.usc.devel",auth_user="moviedo5")
```



<!-- ## Example -->

<!-- This is a basic example which shows you how to solve a common problem: -->

<!-- ```{r example} -->
<!-- ## basic example code -->
<!-- ``` -->